Rare Event Random_Sampling; Model: `r params$Model_Path`;

### 2023-02-10 Non_Identical_r0/Rmarkdown/OSMAC_Model_Free_Method.Rmd
rmarkdown files updated after adding MSE for MLE

Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC_Model_Free/")
load(here(Path,"OSMAC_MF_output.RData"))

@@

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","para_1.gif"))
```

@@

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","Bias_1.gif"))
```

@@

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","U_1.gif"))

@@

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","U_2.gif"))
```

@@

remove(Utility_AM_3,Utility_AM_2,Utility_AM_1,Utility_RM,
       Bias_Vline,Temp_Info,Temp_W,Temp_P,
       Estimated_Vline,Full_model)

@@

@@

@@

@@

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC_MF.RData"))

@@

All_VAR[All_VAR$Model=="Real Model",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[2]]

All_Info[All_Info$Model=="Real Model",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[3]]

All_Bias[All_Bias$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[4]]

All_EMSE[All_EMSE$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[5]]

@@

Accuracy_Data %>%
  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Average Accuracy")+ggtitle("Average Accuracy")->Plot_list[[6]]

ggarrange(plotlist = Plot_list,nrow = 1,ncol = 6,common.legend = TRUE)

>>>>

Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC_Model_Free/")
load(here(Path,"OSMAC_MF_output.RData"))

@@

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","para_1.gif"))
```

@@

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","Bias_1.gif"))
```

@@

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","U_1.gif"))

@@

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","U_2.gif"))
```

@@

remove(Utility_AM_3,Utility_AM_2,Utility_AM_1,Utility_RM,
       Bias_Vline,Temp_Info,Temp_W,Temp_P,
       Full_model)

@@

  # Summarize SMSE MLE
  Est_Parameter_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Model = params$Model_Path ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_RM

  All_MSE_MLE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                       data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
                       data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
                       data.frame("Model"="Assumed Model 3",All_MSE_AM_3))

@@

  # Summarize SMSE MLE
  Est_Parameter_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Model = params$Model_Path ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_RM

  All_MSE_MLE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                     data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
                     data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
                     data.frame("Model"="Assumed Model 3",All_MSE_AM_3))

@@

  # Summarize SMSE MLE
  Est_Parameter_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Estimated_5=Theta4,
                            Model = params$Model_Path ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_RM

  All_MSE_MLE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                     data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
                     data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
                     data.frame("Model"="Assumed Model 3",All_MSE_AM_3))

@@

# Store the Results
save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC_MF.RData"))

@@

All_MSE_MLE[All_MSE_MLE$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency for MLE")->Plot_list[[2]]

All_VAR[All_VAR$Model=="Real Model",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[3]]

All_Info[All_Info$Model=="Real Model",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[4]]

All_Bias[All_Bias$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[5]]

All_EMSE[All_EMSE$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[6]]

@@

Accuracy_Data %>%
  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Average Accuracy")+ggtitle("Average Accuracy")->Plot_list[[7]]

ggarrange(plotlist = Plot_list,nrow = 1,ncol = 7,common.legend = TRUE)

### 2023-02-10 Non_Identical_r0/Rmarkdown/RE_Random_Sampling.Rmd
rmarkdown files updated after adding MSE for MLE

```{r Load Data RM}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"RE_Random_Sampling","Real_Model/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

```{r Load Data AM 1}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"RE_Random_Sampling","Assumed_Model_1/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

```{r Load Data AM 2}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"RE_Random_Sampling","Assumed_Model_2/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

```{r Load Data AM 3}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"RE_Random_Sampling","Assumed_Model_3/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots","para_1.gif"))
```

@@

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots","Bias_1.gif"))
```

@@

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots","U_1.gif"))

@@

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"RE_Random_Sampling","Plots","U_2.gif"))
```

@@

@@

@@

@@

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_RE_RS.RData"))
```

@@

```{r Final plots 1,fig.width=6,fig.height=24}
Plot_list<-list()
All_MSE %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("SMSE")+ggtitle("SMSE Comparison")->Plot_list[[1]]

All_VAR %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[2]]

All_Info %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[3]]

All_Bias %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[4]]

All_EMSE %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[5]]

Accuracy_Data %>% 
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Accuracy")+ggtitle("Average Accuracy")->Plot_list[[6]]

ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
```

@@

All_VAR %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[2]]

All_Info %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[3]]

All_Bias %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[4]]

All_EMSE %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[5]]

@@

Accuracy_Data %>% 
  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Average Accuracy")+ggtitle("Average Accuracy")->Plot_list[[6]]

ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
```

>>>>

```{r Load Data RM}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"RE_Random_Sampling","Real_Model/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

```{r Load Data AM 1}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"RE_Random_Sampling","Assumed_Model_1/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

```{r Load Data AM 2}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"RE_Random_Sampling","Assumed_Model_2/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

```{r Load Data AM 3}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"RE_Random_Sampling","Assumed_Model_3/")
load(here(Path,"RE_Random_Sample_output.RData"))

@@

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots","para_1.gif"))
```

@@

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots","Bias_1.gif"))
```

@@

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots","U_1.gif"))

@@

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"RE_Random_Sampling","Plots","U_2.gif"))
```

@@

  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
        group_by(Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE_MLE

@@

  # Summarize SMSE MLE
  Est_Parameter %>%
        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
        group_by(Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE_MLE

@@

  # Summarize SMSE MLE
  Est_Parameter %>%
        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
        group_by(Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Estimated_5=Theta4,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE_MLE

@@

# Store the Results
save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_RE_RS.RData"))
```

@@

```{r Final plots 1,fig.width=6,fig.height=24}
Plot_list<-list()

All_MSE %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("SMSE")+ggtitle("SMSE Comparison")->Plot_list[[1]]

All_MSE_MLE %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("SMSE")+ggtitle("SMSE Comparison for MLE")->Plot_list[[2]]

All_VAR %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[3]]

All_Info %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[4]]

All_Bias %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[5]]

All_EMSE %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[6]]

Accuracy_Data %>% 
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Accuracy")+ggtitle("Average Accuracy")->Plot_list[[7]]

ggarrange(plotlist = Plot_list,nrow = 7,ncol = 1,common.legend = TRUE)
```

@@

All_MSE_MLE %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency for MLE")->Plot_list[[2]]

All_VAR %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[3]]

All_Info %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[4]]

All_Bias %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[5]]

All_EMSE %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[6]]

@@

Accuracy_Data %>% 
  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Average Accuracy")+ggtitle("Average Accuracy")->Plot_list[[7]]

ggarrange(plotlist = Plot_list,nrow = 7,ncol = 1,common.legend = TRUE)
```
